Inferring the effective start dates of non-pharmaceutical interventions during \covid outbreaks

### 2021-01-27 ms/ms.tex
revise format for bmc

% Introduction
\section*{Introduction}

@@

@@

%\pagebreak
% Discussion
\section*{Discussion}

@@

%\pagebreak
% Models and Methods
{\small
\section*{Models and Methods}

We also plot posterior predictions: we sample 1,000 parameter vectors from the posterior distribution $P(\theta \mid \vec{X})$ fitted to data up to Apr~11, use these parameter vectors to simulate the SEIR model (\autoref{eq:model}) up to Apr~24, and plot the predicted dynamics~(\autoref{fig:ppc}).
Both the accuracy (i.e. overlap of data and prediction) and the precision (i.e. the tightness of the predictions) are good ways to visually compare models.
We also compute the expected posterior RMSE (root mean squared error) of these predictions~(\autoref{table:RMSE}).
} % small

@@

\textbf{Availability of data and materials.} We use Python 3 with NumPy, Matplotlib, SciPy, Pandas, Seaborn, and emcee.
Source code will be publicly available under a permissive open-source license at \href{http://github.com/yoavram-lab/EffectiveNPI}{github.com/yoavram-lab/EffectiveNPI}.
We used freely available data, see source code repository and above \emph{Data} section for details.

>>>>

% Background
\section*{Background}

@@

% Methods
\section*{Methods}

We also plot posterior predictions: we sample 1,000 parameter vectors from the posterior distribution $P(\theta \mid \vec{X})$ fitted to data up to Apr~11, use these parameter vectors to simulate the SEIR model (\autoref{eq:model}) up to Apr~24, and plot the predicted dynamics~(\autoref{fig:ppc}).
Both the accuracy (i.e. overlap of data and prediction) and the precision (i.e. the tightness of the predictions) are good ways to visually compare models.
We also compute the expected posterior RMSE (root mean squared error) of these predictions~(\autoref{table:RMSE}).

@@

% Discussion and Conclusions
\section*{Discussion and Conclusions}

@@

% Abbreviations
{\small
\section*{Abbreviations}
NPI: non-pharmaceutical interventions, CI: credible interval, MCMC: Markov chain Monte Carlo, SEIR: susceptible-exposed-infected-recovered, WAIC: widely applicable information criterion, RMSE: root mean squared error, IAT: integrated autocorrelation time, \covid: coronavirus disease 2019, \sars: severe acute respiratory syndrome coronavirus 2.
}

@@

\textbf{Availability of data and materials.} We use Python 3 with NumPy, Matplotlib, SciPy, Pandas, Seaborn, and emcee.
Source code will be publicly available under a permissive open-source license at \href{http://github.com/yoavram-lab/EffectiveNPI}{github.com/yoavram-lab/EffectiveNPI}.
Data for Wuhan, China, retrieved from \citet{Pei2020}.
Data for 11 European countries retrieved from \citet{Flaxman2020}.
